---
title: "Weight of Fish"
author: "David Acevedo"
date: "`r Sys.Date()`"  
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5

 
    
---


```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
require(car)
require(leaps)
```

# Predicting Fish Weight
```{r}
fish <- read.csv(file = "Fish.csv")
```

```{r eval=TRUE}
 
fish <- fish %>%
mutate(across(where(is.character), as.factor))
levels(fish$Species)
Bream <- filter(fish, Species == "Bream")
Bream <- select(Bream, -Species) 
Parkki <- filter(fish, Species == "Parkki")
Parkki <- select(Parkki, -Species) 
Perch <- filter(fish, Species == "Perch")
Perch <- select(Perch, -Species) 
Pike <- filter(fish, Species == "Pike")
Pike <- select(Pike, -Species) 
Roach <- filter(fish, Species == "Roach")
Roach <- select(Roach, -Species) 
Smelt <- filter(fish, Species == "Smelt")
Smelt <- select(Smelt, -Species) 
Whitefish <- filter(fish, Species == "Whitefish")
Whitefish <- select(Whitefish, -Species) 
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r}
require(tidyverse)
if(!require("Bolstad")) {install.packages("Bolstad");require("Bolstad")}

data(bears)
Bears <- select(bears,contains("e"),-Name)
#Clean missing values out of dataset (needed to run Anova at end of demo)
Bears<- na.omit(Bears)
```

# For each of the three species of fish listed below, determine the best regression model and also the best 2 element regression model. Use the BestSubset Regression helper file.


## Perch
```{r}
library(leaps)
regsubsets.out <- regsubsets(Weight ~ ., data = Perch, nbest = 1, nvmax = NULL, force.in = NULL, force.out =NULL, method= "exhaustive") 
summary.out <-summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2" ,legend= "bottom" , main = "Adjusted R^2")
```
### Best Models

### Best Two regressor model
Using leaps we were able to locus is power onto tne adjusted (Squared value. Then a woud give us only the nionest or adjusted r squared values. Using leaps we were able to focus its power onto the adjusted r-squared value. Then it would give us only the highest of adjusted r squared values for 1, 2, 3, 4 and 5 variables for pike. Using this kind of leaps & shows thal L1 and L3 are the best two regressors for the highest adjusted r-squared
value making it the best two regressor model

## Pike
```{r}
library(leaps)regsubsets.out<- regsubsets(Weight~.,data=Pike, nbest = 1, nvmax = NULL, force.in = NULL, force.out = NULL,method= "exhuastive")
summary.out





```
### Best Models

### Best Two regressor model
Using leaps we were able to focus its power onto the adjusted r-squared value.
Then it would give us only the highest of adjusted r-squared values for 1, 2,
3, 4 and 5 variables for pike. Using this kind of leaps it shows that L1 and
L3 are the best two regressors for thel highest adjusted r-squared value making
it the best two regressor model.
## Roach

### Best Models

### Best Two regressor model

## Final Summary Statements